### 2022-03-28 paper/localpsf.tex
about to reorganize intro based on Noemi's suggestions

	}
	\caption{Construct product-convolution H-matrix}
	\label{alg:construct_Atilde}
\end{algorithm2e}

@@

	\Input{Finite set of candidate points $P\subset \Omega$, \\spatially varying mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, \\domain boundary information $\partial \Omega$, \\previous sample point batches $\pointbatch_1, \dots, \pointbatch_{k-1}$}
	\Output{Batch of new sample points $\pointbatch_k$}

@@

		\If{$E_p \cap E_q \neq \{\}$ for all $q \in \pointbatch_k$ and $E_p \cap \partial \Omega = \{\}$}{
			\tcp{$E_p$ and $E_q$ are the ellipsoids defined in \eqref{eq:support_ellipsoid}}

>>>>

	}
	\caption{Construct H-matrix approximation}
	\label{alg:construct_Atilde}
\end{algorithm2e}

@@

	\Input{Finite set of candidate points $P\subset \Omega$, \\spatially varying mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, \\previous sample point batches $\pointbatch_1, \dots, \pointbatch_{k-1}$}
	\Output{Batch of new sample points $\pointbatch_k$}

@@

		\If{$E_p \cap E_q \neq \{\}$ for all $q \in \pointbatch_k$}{
			\tcp{$E_p$ and $E_q$ are the ellipsoids defined in \eqref{eq:support_ellipsoid}}
